Performing graph-based clustering with rOpenScPCA

### 2024-12-17 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
moar colors

```{r violin silhouette}
ggplot(silhouette_results) +
  aes(x = cluster, y = silhouette_width) +
  geom_violin(fill = "darkolivegreen3") +
  labs(x = "Cluster", y = "Silhouette width")
```

@@

```{r ari density}
ggplot(stability_results) +
  aes(x = ari) +
  geom_density(color = "grey30", fill = "darkolivegreen3") +
  labs(x = "Adjusted rand index across bootstrap replicates")
```

>>>>

```{r violin silhouette}
ggplot(silhouette_results) +
  aes(x = cluster, y = silhouette_width) +
  geom_violin(fill = "darkmagenta") +
  labs(x = "Cluster", y = "Silhouette width")
```

@@

```{r ari density}
ggplot(stability_results) +
  aes(x = ari) +
  geom_density(color = "grey30", fill = "lightslateblue") +
  labs(x = "Adjusted rand index across bootstrap replicates")
```
